---
title: "DATA 607 Project 3"
author: Harris Dupre, Scott Reed, William Outcault, Diane DeOcampo, Stephen Haslett, Samuel Kigamba, Emmanuel Hayble-Gomes
date: "10/17/2019"
output: html_document
---

<style>
  table {
    margin-top: 30px !important;
    margin-bottom: 50px !important;
  }
  pre {
    rgin-bottom: 50px !important;
  }
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, warning=FALSE}
library(DBI)
library(RMariaDB)
library(data.table)
library(dplyr)
library(dbplyr)
library(tidyverse)
library(kableExtra)
library(knitr)
library(stringr)
library(ggplot2)
```

###Connect to the MYSQL database containing the data science meetup and keywords data.###
```{r, eval=TRUE}
con <- dbConnect(MariaDB(),host="data607.mysql.database.azure.com", dbname="data607",username="data607@data607", client.flag = CLIENT_COMPRESS, password="!WORK,open,DOWN!")
```


###Read the "keyword_raw" database table and output the data as Bootstrap table.###
```{r, eval=TRUE}
keywords <- dbReadTable(con, "keyword_raw")
keywords %>% kable() %>% kable_styling(bootstrap_options = c('striped', 'bordered'))
```


###Read the "events" database table and output the data as a Bootstrap table.###
```{r, eval=TRUE}
meetup_events <- dbReadTable(con, "events")
meetup_events %>% kable() %>% kable_styling(bootstrap_options = c('striped', 'bordered'), full_width = TRUE) %>%
scroll_box(height = '300px')
```


###Count the occurence of each keyword in the "description" column of the events database table.###
```{r, eval=TRUE}
keyword_scan<-sapply(keywords$Keyword, function(Keyword){str_count(meetup_events$description, Keyword)})

count_results <- setNames(nm=c('Keyword','Frequency'), stack(colSums(keyword_scan))[2:1])
count_results %>% kable() %>% kable_styling(bootstrap_options = c('striped', 'bordered')) %>% row_spec(0, color = "black")
```


###Plot the keyword frequency results as a histogram.###
```{r, message=FALSE, warning=FALSE}
results <- as.data.frame(count_results)

frequency_chart <- ggplot(results, aes(x = reorder(Keyword, -Frequency), y = Frequency, fill = Keyword)) +
                   geom_bar(stat = "identity", position = position_dodge()) +
                   xlab("Keyword") + ylab("Frequency") +
                   theme(axis.text.x = element_text(angle = 90)) +
                   ggtitle("Total Keyword Frequency")
frequency_chart
```

###Close the database connection.###
```{r, eval=TRUE}
dbDisconnect(con)
```