---
title: "Job Listing Keyword Analysis"
author:
date: "10/20/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Introduction

The goal of this analysis will be to determine the relative appearance of keywords in job listings on Monster, SimplyHired, LinkedIn, and Indeed.

The idea for this analysis came from the following article that discusses the most in-demand skills by employers seeking data scientists:
https://towardsdatascience.com/the-most-in-demand-skills-for-data-scientists-4a4a8db896db

The raw data is provided in the following Google Sheet:
https://docs.google.com/spreadsheets/d/1df7QTgdAOItQJadLoMHlIZH3AsQ2j2_yoyvHOpsy9qU/edit#gid=1072460513

```{r message=FALSE}
library(tidyr)
library(dplyr)
library(RMariaDB)
library(stringr)
library(stringi)
library(ggplot2)
```

#### Importing, Loading to Database, Tidying

```{r}

keyword_raw <- read.csv("data_science_keywords.csv", header=TRUE, sep=",")

con <- dbConnect(MariaDB(), host="data607.mysql.database.azure.com", dbname="data607",username="data607@data607", client.flag = CLIENT_COMPRESS, password="!WORK,open,DOWN!")

dbWriteTable(con,"keyword_raw",keyword_raw, overwrite=TRUE)

keyword_tidy <- gather(keyword_raw, "Site", "Frequency",2:5)
keyword_tidy$Frequency<- as.numeric(gsub(",","",keyword_tidy$Frequency))
keyword_tidy

dbWriteTable(con, "keyword_tidy", keyword_tidy, overwrite=TRUE)


```

#### Transformation for Analysis

```{r}
keyword_analysis <- group_by(keyword_tidy, Keyword)
keyword_analysis <- summarize(keyword_analysis, Sum_Frequency = sum(Frequency))
keyword_analysis <- mutate(keyword_analysis, Total=sum(Sum_Frequency))
keyword_analysis <- mutate(keyword_analysis, Pct_Frequency=round(Sum_Frequency/Total,3)*100)
analysis_df <-as.data.frame(keyword_analysis)

dbWriteTable(con,"keyword_analysis_df",analysis_df, overwrite=TRUE)
```

#### Plotting Data

```{r}
ggplot(analysis_df, aes(x=Keyword,y = Pct_Frequency)) +
  geom_bar(width = .75,stat = "identity", position="dodge") +
  ggtitle("Relative Frequency of Keywords In Data Science Job Listings", subtitle="Sites: Monster, SimplyHired, Indeed, LinkedIn") +
  labs(x="Keyword",y="Percentage") +
  theme(plot.title = element_text(hjust=0.5),plot.subtitle=element_text(hjust=0.5),axis.text.x = element_text(angle = 90,hjust=1,vjust=.5)) +
  scale_y_continuous(breaks = seq(0,25,by = 1))

dbDisconnect(con)
```